Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-21 analysis/paper/paper.Rmd
Example of next code chunks to work on in paper.Rmd, and modified survey_timing to clarify what next steps are needed. (updated with some additions Feb 21)

*Target Frame* - space, time, scale, target populations
*Spatial* Upper Lynn Canal visible from coastline from Skagway to Dyea, including Skagway & Taiya river mouths and Nahku Bay (between Skagway and Dyea Point)

@@

Incidental: 48 other spp
Questions: are these all migratory? Any year-round residents? Any of special concern? 
Any especially problematic for detection on water or identification of spp?

>>>>

*Target Frame* - space, time, scale, target populations

*Spatial* Upper Lynn Canal visible from coastline from Skagway to Dyea, including Skagway & Taiya river mouths and Nahku Bay (between Skagway and Dyea Point)

> INSERT FIGURE FROM NRSS report

@@

Incidental: 48 other spp

> Consider graphic of spp frequency of occurrence (maybe some panel-rich figure, one panel per spp, showing annual average percentage of daily observations in which spp was sighted - as line-connected points?- ordered from most frequently observed spp to least frequently. Think about appropriate estimator so annual value accounts for variation in survey effort across years.) likely needs to be a full page figure (e.g., we'll need to set  fig.width and fig.height)

```{r EDA_AllSpp_Frequency, eval=TRUE, cache = FALSE, include = FALSE}
# lets discuss what I'm thinking of. It is of secondary importance, so don't want this 
# to consume tons of your time.

#source("../scripts/survey_timing_EDA.R", echo=FALSE)

```{r Fig-AllSppFreq, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="blah blah about consistency in target species occurrence. Maybe something about new spp showing up?"}

#print(Plot1)
```

Questions: are these all migratory? Any year-round residents? Any of special concern? 
Any especially problematic for detection on water or identification of spp?
